Skip to content
Search or jump to…

Pull requests
Issues
Marketplace
Explore
 
@hussein-mohsen 
Learn Git and GitHub without any code!
Using the Hello World guide, you’ll start a branch, write comments, and open a pull request.


13
00gersteinlab/TH2 Private
 Code Issues 0 Pull requests 0 Actions Projects 0 Wiki Security Insights Settings
TH2/scripts/variant_scripts/generate_ENSEMBL_to_Gene_ID_list.Rmd
@invalid-email-address invalid-email-address Pushed code.
3843cd9 on Aug 16, 2018
51 lines (36 sloc)  1.62 KB
  
---
title: "ENSEMBL_to_Gene_ID"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# METHOD 1: biomaRt Package
# Helpful link: https://www.bioconductor.org/packages/devel/bioc/vignettes/biomaRt/inst/doc/biomaRt.html#selecting-a-biomart-database-and-dataset
library(biomaRt)
grch37 = useMart(biomart="ENSEMBL_MART_ENSEMBL", host="grch37.ensembl.org", path="/biomart/martservice")
# double check by listing the datasets in R
listDatasets(grch37)
# choose the Human dataset in R
ensembl_grch37 <- useDataset("hsapiens_gene_ensembl", mart=grch37)
# list available attributes in the Mart
listAttributes(ensembl_grch37)
# Fetch the genes (ENSEMBL gene IDs and gene names) in R
genes.with.length.info <- getBM(attributes=c("ensembl_gene_id", "external_gene_name", "entrezgene_id", "chromosome_name", "start_position", "end_position"), values="*", mart=ensembl_grch37)
genes.with.length.info$length <- abs(genes.with.length.info$end - genes.with.length.info$start)

# save the file
write.table(genes.with.length.info, "GRCh37_bioMart_bioConductor_package_all_121819.txt", sep="\t", row.names = FALSE, quote = FALSE)
```

```{r}
# METHOD 2: Homo.sapiens Package
library(Homo.sapiens)
# get key types
keytypes(Homo.sapiens)
# choose "ENSEMBL" and save all keys
ENSEMBL_keys_all <- keys(Homo.sapiens, keytype="ENSEMBL")
length(ENSEMBL_keys_all)
# get all gene names and ENSEMBL IDs
gene_symbol_vs_ENSEMBL_ID_all <- AnnotationDbi::select(Homo.sapiens, keys=ENSEMBL_keys_all, keytype="ENSEMBL", columns=c("SYMBOL"))
# save the file
write.table(gene_symbol_vs_ENSEMBL_ID_all, "ENSEMBL_ID_vs_gene_ID_GRCh37_Homosapiens_bioConductor_package_all.txt", sep="\t", col.names = c("ENSEMBL_ID", "Gene_Symbol"), row.names=FALSE, quote = FALSE)
```

